???Grape Quality and its Link to Regional Differences in the Australian Winegrowing Industry

### 2023-08-31 article.tex
discussion and comments

% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program, which aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by the SWA is entered manually by winegrowers using a web based interface tool. A total of 6091 observations were collected from 2012 to 2022. Each observation contained 23 variables reflecting a vineyards account for the given year (see Table \ref{tab:vars}).
\par
\begin{table}[] 
  \label{tab:vars}
  \caption{Summary of variables used in the analysis. The recorded column indicate values that were either greater than zero or that were not missing.}\label{tab:summary}
  \begin{tabular}{@{}ccccl@{}}
    \toprule
    \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ Classes\end{tabular}} &  \\ \midrule
    Water Used & Mega Litres & 5846 &  &  \\
    Diesel & Litres & 5585 &  &  \\
    Biodiesel & Litres & 25 &  &  \\
    LPG & Litres & 958 &  &  \\
    Herbicide Spray & Times per year & 2026 &  &  \\
    Year & Class & 6091 & 10 &  \\
    Disease & Class & 6091 & 2 &  \\
    Region & Class & 6091 & 58 &  \\
    Solar & Kilowatt Hours & 622 &  &  \\
    Irrigation Type & Class & 6091 & 20 &  \\
    Petrol & Litres & 4309 &  &  \\
    Slashing & Times per year & 2290 &  &  \\
    Yield & Tonnes & 5935 &  &  \\
    Irrigation Energy & Class & 6091 & 16 &  \\
    Area Harvested & Hectares & 6091 &  &  \\
    Electricity & Kilowatt Hours & 1015 &  &  \\
    Insecticide Spray & Times per year & 1092 &  &  \\
    Fertiliser & \begin{tabular}[c]{@{}c@{}}Kilograms \\ of Nitrogen\end{tabular} & 795 &  &  \\
    Fungicide Spray & Times per year & 2260 &  &  \\
    Cover Crop & Class & 6091 & 32 &  \\
    Water Type & Class & 6091 & 39 &  \\
    Profit & AUD & 853 &  &  \\
    Operating Costs & AUD & 853 &  &  \\ \bottomrule
    \end{tabular}
\end{table}

The data originally contained only two multiclass variables: year and region. Variables that measured the same metric from different sources (such as water collected from rivers versus water from dams) were converted into multiclass variables representing the source. The total amount used from these variables was retained as a separate variable. Occurrences of multiple sources were defined as separate classes. As harvest does not run by calendar year, years are in financial years. Region represents one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}. Profit was also used as a binary variable, depicting whether a vineyard was profitable or not.
\par
%
% Mention one-hot-encoding.
%

%
% How deep into the classes do we go?
%
\subsection{XGBoosted Trees}
XGBoosted (eXtreme Gradient Boosting) trees were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. They were chosen for this analysis as they provide both a high predictive performance and ability to effectively capture complex relationships. An XGBoosted tree was created for each variable to show how they interacted. Each tree included all but the economic variables (profit and operating cost), which were only included once as predicted variables.
\par
Following Chen and Guestrin \citep{chenXGBoostScalableTree2016}, XGboosted trees predict a value $y_i$ from the input $x_i$. The method of prediction is achieved through a tree ensemble model, using $K$ additive functions to predict the output.

@@

with the tree structure defined using left $I_L$ and right $I_R$ instance sets of nodes, with $I = I_L \cup I_R$. Instead of enumerating all possible tree structures, a greedy algorithm iteratively adds branches to the tree minimising $ \mathcal{L}_{split} $ in (\ref{eqn:enumerate}). The frequency of a variable's occurrence within a tree is directly attributed to the minimisation of the objective function (or loss) through the minimisation of  $ \mathcal{L}_{split} $.
\par
The frequency of a variable appearing as a node within the ensemble was used as a measure of importance. This measure was chosen as it connected a variable to the minimisation of its associated objective function, translating the value into a simple count metric. Creating XGBoosted trees for each variable allowed the use of importance to show how strongly variables were associated with each other. The importance of predictor variables to economic variables was illustrated through the use of Sankey diagrams constructed using the Holoviews python library \citep{philipp_rudiger_2020_3904606}. Other variable's interconnectedness was demonstrated through the use of a chord diagram also created using Holoviews.
\par
Each variable utilised 80\% of the data to train the XGBoost ensemble, with 20\% reserved for testing and validation. Testing was done through the iterative minimisation of the respective objective function for the variables type. For continuous variables 20\% was used as testing data, minimising the root-mean-square function. The final model was validated using repeated k-fold cross validation for 10 folds, repeated 10 times.
 For  binary and multiclass variables data was split into 80\% training, 10\% testing and 10\% validation data. Due to class disparity in multiclass variables (most prominently in region) data was stratified into each subset at the same ratio of class occurrence. Validation was summarised through confusion matrices and their associated accuracy 
\par
The use of the XGBoost library incorporates regularisation techniques built into the software to mitigate over-fitting and enhance model generalisation. The further use of cross validated grid search functions allowed for the selection of better performing hyperparameters when selecting the final model. The performance measure for model selection was root-mean-square error for continuous variables. The receiver operator characteristic's area under the curve was used for category variables \citep{hanley1982meaning}. Multiclass variables utilised the one verse one approach to minimise sensitivity to class disparity \citep{ferriExperimentalComparisonPerformance2009,handSimpleGeneralisationArea2001}.

@@

Classification and Regression Trees were created for region, year, profit and operating cost. These models describe the partitions that are useful in predicting these variables; giving insight into the trees that make up the ensembles created by XGBoost. These trees were created using the rparts and caret packages \citep{kuhnBuildingPredictiveModels2008,terrytherneauRpartRecursivePartitioning2022} in the R statistical programming language \citep{rcoreteamLanguageEnvironmentStatistical2021}.
\par
Classification trees were validated using K-fold cross validation. Each model was validated using 10 folds, utilising a random selection of different samples ten separate times to validate each of the  classification trees. A summary confusion matrix was then constructed to show the class bias and overall accuracy of each tree.

@@

Region classification performed at 36.10\% and 56.82\% accuracy, for the classification tree and XGBoosted ensemble respectively. The most prominent features used to classify regions with the classification tree was water sources (see Figure \ref{fig:region_tree}). This differed from the variables that illustrated the greatest importance for the XGBoosted ensemble (see Figure (\ref{fig:region_sankey}), with predictor variables being highly interrelated in importance. Area, water, fuel and yield were more determining factors when predicting region using XGBoost. Although water and diesel were two of the three most frequently occurring variables in predicting region, they were not as connected to the other predictor variables as Yield and area harvested were.
\par
It is reasonable that regions, being subjected to different rainfalls and temperatures, would require different amounts of water, and would have access to different water sources. The relation of area harvested and fuel (particularly petrol) is prominent with other predictors. Due to the wide variety of uses of petrol and diesel, it is likely that they are representative of other activities within the vineyard, such as pruning and harvesting. With predictors such as yield and area being highly interconnected as they likely operate as proxy variables to other factors, possibly other present variables.
\par
Many of the regions had significantly lower reporting rates, resulting much poorer classification performance. The regions with the most samples performed the best. Notably bordering regions were routinely grouped together and misclassified as the same region. Two areas taht suffered the most from this, specifically with the classification tree were the lime coast (cool coastal areas in South Australia) and the warmer inland regions along the Murray Darling. The classification tree likely had more difficulty discerning vineyards closer to the river using only water sources due to the greater access to river water in these areas.
%, for example the two closest regions to Coonawarra, Padthaway and Wrattonbulley, were misclassified as Coonawarra even though they had 147 and 137 samples respectively. The same case was found for the Murray Darling, with 143 samples, it was misclassified as the Riverland. These misclassifications are likely due to the incredibly similar regional properties and close proximity these regions have with one another. Other misclassifications were most likely due to lower reporting rates with many regions being under represented.

@@

The classification tree and XGBoosted ensemble performed similarly for classifying year with 41.15\% and 51.81\% respectively. Electricity and the type of irrigation were highly influential within the classification tree. Similarly, electricity was the most frequently occurring node in the XGBoost ensemble. However, other variables such as slashing passes, and fungicide and herbicide spraying were more prevalenct than in the classification tree. Weed and disease outbreaks are likely an influential factor when classifying different years, making the decisions to spray and slash unique factors that differ year to year. Climatic differences between years are likely tied to the influence of yield and water use.
\par
Over half of the interrelated importance of the predictor variables is dominated by area harvested, yield and slashing passes. Although all the predictor variables are highly connected, their relative importance is not as prominent as the three major variables. It is of particular note of the relative importance of slashing to area, fuel and yield; as these are not directly related activities. The connection between slashing and spraying is that those who do a set number of spraying or slashing passes tended to do that many passes for all slashing and spraying activities.

@@

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{operating_costs.pdf}}
  \caption{Decision tree predicting Operating Costs. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:operating_costs_tree}
\end{figure}

@@

@@

\subsection{Validation}

\begin{table}[]
  \caption{Validation and training accuracies of each multiclass variable.}
  \begin{tabular}{@{}ccc@{}}
  \toprule
  \textbf{Variable} & \textbf{Validation} & \textbf{Training} \\ \midrule
  \textbf{cover crops} & 0.364086 & 0.396418 \\
  \textbf{water type} & 0.742097 & 0.928905 \\
  \textbf{profitable} & 0.705882 & 0.719737 \\
  \textbf{irrigation type} & 0.841845 & 0.847554 \\
  \textbf{giregion} & 0.505824 & 0.568242 \\
  \textbf{irrigation energy} & 0.746293 & 0.836405 \\
  \textbf{data year id} & 0.422003 & 0.518059 \\ \bottomrule
  \end{tabular}
  \end{table}

\subsection{Model 1 GI Regions}

The first Model was used to classify GI regions % Interestingly the firs I am hearing of this - each model needs to be more well summarised. A table would be good.
and resulted in an accuracy of 36.48\% across 52 classes. The most prominent features used to classify regions were the types of water resources available (see Figure 1). Two regions, the Riverland and Coonawarra, were the most accurate classes being 92.74\% and 96.97\% respectively.
% it might be worth only talking about the regions that were well classifified - and then talk about their determining traits.
These regions differ greatly in practice and geophysical properties, with the Riverland being a dry warm inland region and Coonawarra being a cooler, wet coastal region. However, they are both similar in operational scales, with vineyards being relatively large compared with other regions.
%Summary statistics regarding these two regions would be a better point of comparison, for example:
%
% How much in size do these operational scales differ?
% How much yield do they differ by?
% What are the differences in rainfall etc
% What makes them unique, different and similar?
%
The differences in resources and practices between these regions are also significant, such as the Riverland utilising the river Murray as a water source.
% What are the specific differences? This is a really critical part of this paper
Many of the regions had significantly lower reporting rates, resulting much poorer classification performance. % This is almost its own paragraph. Why was this case? is it important? what are the similarities and differences of regions that were poorly classified?
 The regions with the most samples performed the best (see Table 1). Notably bordering regions were routinely grouped together and misclassified as the same region, for example the two closest regions to Coonawarra, Padthaway and Wrattonbulley, were misclassified as Coonawarra even though they had 147 and 137 samples respectively. The same case was found for the Murray Darling, with 143 samples, it was misclassified as the Riverland.
 % THis speaks highly to why regions were poorly classified.
These misclassifications are likely due to the incredibly similar regional properties and close proximity these regions have with one another. Other misclassifications were most likely due to lower reporting rates with many regions being under represented.

>>>>

% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program, which aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by the SWA is entered manually by winegrowers using a web based interface tool. A total of 6091 observations were collected from 2012/2013 to 2021/2022 financial years. 23 variables were used for each observation reflecting a vineyards account for the given year (see Table \ref{tab:vars}). The profit variable was additionally transformed and included as another separate variable, profitable; depicting whether a vineyard was profitable or not.
\par

\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate values that were either greater than zero or that were not missing.}\label{tab:summary}
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ Classes\end{tabular}} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6091 & 10 & \\
  Disease & Class & 6091 & 2 & \\
  Region & Class & 6091 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6091 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6091 & 16 & \\
  Area Harvested & Hectares & 6091 & & \\
  Electricity & Kilowatt Hours & 1015 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & \begin{tabular}[c]{@{}c@{}}Kilograms \\ of Nitrogen\end{tabular} & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6091 & 32 & \\
  Water Type & Class & 6091 & 39 & \\
  Profit & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}

The data originally contained only two multiclass variables: year and region. Variables that measured the same metric from different sources (such as water collected from rivers versus water from dams) were converted into multiclass variables representing the source. The total amount used from these variables was retained as a separate variable. Occurrences of multiple sources were defined as separate classes. 
\par
The variable region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par
%
% Mention one-hot-encoding.
%

%
% How deep into the classes do we go?
%
\subsection{XGBoosted Trees}
XGBoosted (eXtreme Gradient Boosting) trees were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. They were chosen for this analysis as they provide both a high predictive performance and ability to effectively capture complex relationships. An XGBoosted tree was created for each variable to show how they interacted. Each tree included all but the economic variables (profit and operating cost), which were only included once as response variables.
\par
Following Chen and Guestrin \citep{chenXGBoostScalableTree2016}, XGboosted trees predict a value $y_i$ from the input $x_i$. The method of prediction is achieved through a tree ensemble model, using $K$ additive functions to predict the output.

@@

with the tree structure defined using left $I_L$ and right $I_R$ instance sets of nodes, with $I = I_L \cup I_R$. Instead of enumerating all possible tree structures, a greedy algorithm iteratively adds branches to the tree minimising $ \mathcal{L}_{split} $ in (\ref{eqn:enumerate}). The frequency of a variable's occurrence within a tree is directly attributed to the minimisation of the objective function (or loss) through the minimisation of $ \mathcal{L}_{split} $.
\par
The frequency of a variable appearing as a node within the ensemble was used as a measure of importance. This measure was chosen as it connected a variable to the minimisation of its associated objective function, translating the value into a simple count metric. Creating XGBoosted trees for each variable allowed the use of importance to show how strongly variables were associated with each other. The importance of predictor variables to economic variables was illustrated through the use of Sankey diagrams constructed using the Holoviews python library \citep{philipp_rudiger_2020_3904606}. Other variable's interconnectedness was demonstrated through the use of a chord diagram also created using Holoviews.
\par
Each variable utilised 80\% of the data to train the XGBoost ensemble, with 20\% reserved for testing and validation. Testing was done through the iterative minimisation of the respective objective function for the variables type. For continuous variables 20\% was used as testing data, minimising the root-mean-square function. The final model was validated using repeated k-fold cross validation for 10 folds, repeated 10 times. $R^2$ scores were used to determine the best regression models during validation.
For binary and multiclass variables data was split into 80\% training, 10\% testing and 10\% validation data. Due to class disparity in multiclass variables (most prominently in region) data was stratified into each subset at the same ratio of class occurrence. Validation was summarised through the accuracy, the proportion of true negatives and positives.
\par
The use of the XGBoost library incorporates regularisation techniques built into the software to mitigate over-fitting and enhance model generalisation. The further use of cross validated grid search functions allowed for the selection of better performing hyperparameters when selecting the final model. The performance measure for model selection was root-mean-square error for continuous variables. The receiver operator characteristic's area under the curve was used for category variables \citep{hanley1982meaning}. Multiclass variables utilised the one verse one approach to minimise sensitivity to class disparity \citep{ferriExperimentalComparisonPerformance2009,handSimpleGeneralisationArea2001}.

@@

Classification and Regression Trees were created for region, year, profit and operating cost. These models describe the partitions that are useful in predicting these variables; giving insight into the trees that make up the ensembles created by XGBoost. These trees were created using the rparts and caret packages \citep{kuhnBuildingPredictiveModels2008,terrytherneauRpartRecursivePartitioning2022} in the R statistical programming language \citep{rcoreteamLanguageEnvironmentStatistical2021}.
\par
Decision trees were validated using K-fold cross validation. Each model was validated using 10 folds, utilising a random selection of different samples ten separate times to validate each of the decision trees. The same measure of accuracy as the XGBoosted trees was used for comparison.

@@

Region classification performed at 32.34\% (3.67\% standard deviation) and 56.82\% accuracy (50.58\% validation accuracy), for the classification tree and XGBoosted ensemble respectively. The most prominent feature used to classify regions with the classification tree was water source (see Figure \ref{fig:region_tree}). This differed from the variables that illustrated the greatest importance for the XGBoosted ensemble (see Figure (\ref{fig:region_sankey}), with predictor variables being highly interrelated in importance. Area, water, fuel and yield were more determining factors when predicting region using XGBoost. Although water and diesel were two of the three most frequently occurring variables in predicting region, they were not as connected to the other predictor variables as Yield and area harvested were.
\par
It is reasonable that regions, being subjected to different rainfalls and temperatures, would require different amounts of water, and would have access to different water sources. The relation of area harvested and fuel (particularly petrol) is prominent with other predictors. Due to the wide variety of uses of petrol and diesel, it is likely that they are representative of other activities within the vineyard, such as pruning and harvesting. With predictors such as yield and area being highly interconnected as they likely operate as proxy variables to other factors, possibly other present variables.
\par
Many of the regions had significantly lower reporting rates, resulting in much poorer classification performance. The regions with the most samples performed the best. Notably bordering regions were routinely grouped together and misclassified as the same region. Two areas that suffered the most from this, specifically with the classification tree were the Limestone Coast (cool coastal areas in South Australia) and the warmer inland regions along the Murray Darling. The classification tree likely had more difficulty discerning vineyards closer to the river using only water sources due to the greater access to river water in these areas.
%, for example the two closest regions to Coonawarra, Padthaway and Wrattonbulley, were misclassified as Coonawarra even though they had 147 and 137 samples respectively. The same case was found for the Murray Darling, with 143 samples, it was misclassified as the Riverland. These misclassifications are likely due to the incredibly similar regional properties and close proximity these regions have with one another. Other misclassifications were most likely due to lower reporting rates with many regions being under represented.

@@

The classification tree and XGBoosted ensemble performed similarly for classifying year with 35.20\% (6.28\% standard deviation) and 51.81\% (42.20\% validation accuracy) respectively. Electricity and the type of irrigation were highly influential within the classification tree. Similarly, electricity was the most frequently occurring node in the XGBoost ensemble. However, other variables such as slashing passes, and fungicide and herbicide spraying were more prevalenct than in the classification tree. Weed and disease outbreaks are likely an influential factor when classifying different years, making the decisions to spray and slash unique factors that differ year to year. Climatic differences between years are likely tied to the influence of yield and water use.
\par
Over half of the interrelated importance of the predictor variables is dominated by area harvested, yield and slashing passes. Although all the predictor variables are highly connected, their relative importance is not as prominent as the three major variables. It is of particular note of the relative importance of slashing to area, fuel and yield; as these are not directly related activities. The connection between slashing and spraying is that those who do a set number of spraying or slashing passes tended to do that many passes for all slashing and spraying activities.

@@

There was a pronounced difference in accuracy between the regression tree and the XGBoost model when predicting Operating costs. With the regression tree achieving an $R^2$ of 0.0931 (with a standard deviation of 0.0197) in its cross validation. The XGBoosted regression ensemble achieved an $R^2$ of 0.8025 (with a standard deviation of 0.1033).
\par
Within the XGBoost ensemble's nodes for operating costs (see figure \ref{fig:operating_costs_sankey}) fuel, water, area and yield occurred the most, similarly to region. Both diesel and petrol were of more relative importance (being ranked higher) in operating costs than water was compared with region. It is surprising that electricity, slashing and spraying was not more prominent in operating costs. However, Figure \ref{fig:year_sankey} shows that electricity, slashing and spraying are important variables in determining area and yield. Electricity in particular is used predominantly for irrigation and so is related largely to the size of a vineyard. However, slashing and spraying are measured in discrete tractor passes and show a surprising connection to the overall size of a vineyard, despite not being scaled to any measure of size. This would mean that, although measured as the same increment, a slashing or spraying pass in a larger vineyard would consume more fuel and wages than in a smaller vineyard.

%
% Is there any point in including this if its so bad?
%
% \begin{figure}
%  \resizebox{\textwidth}{!}{
%  \includegraphics{operating_costs.pdf}}
%  \caption{Decision tree predicting Operating Costs. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:operating_costs_tree}
% \end{figure}

@@

Predictions of profit performed poorly compared to operating costs with the regression tree having an $R^2$ of 0.1873 (with a standard deviation of 0.0522) and the XGBoosted ensemble achieving an $R^2$ of 0.2535 (with a standard deviation of 0.3126). The high standard deviation in the XGBoosted tree was a bias in more accurately predicting vineyards that made profit compared to those that lost money.With much higher $R^2$ values being achieved in k-folds containing only those that made profits (recording a maximum of 0.7634).
% profit summary stats
% max 3345000
% min -3937878
% std 396027.633119089
% range 7282878
\par
There was a disparity of 66.63\% of vineyards recording a profit than those that did not. When predicting if a vineyard would be profitable or not the classification tree and XGBoosted ensemble did not perform considerably differently from this proportion. With the regression tree achieving an accuracy of 68.66\% (and a standard deviation of 0.01\%) and the XGBoost ensemble achieving 71.97\% accuracy (with a validation accuracy of 70.59\%).
\par
It was surprising that operating costs performed substantially better in $R^2$ compared to profit. Interestingly the important variables when attempting to determine profit were similar to those used to classify region (see Figure \ref{fig:profit_sankey}), with the exception of water used. Both the regression tree and the XGBoosted ensemble used region, specifically the Hunter Valley. The regression tree also used Tasmania when determining profit. Both the Hunter valley and Tasmania are known for the production of high quality grapes used in export wines \citep{wineaustraliaNationalVintageReport2022}. A major difference between region and profit was the importance given to water use, with water use being a more important variable in predicting region than profit.

@@

% \begin{table}[]
%  \caption{Validation and training accuracies of each multiclass variable.}
%  \begin{tabular}{@{}ccc@{}}
%  \toprule
%  \textbf{Variable} & \textbf{Validation} & \textbf{Training} \\ \midrule
%  \textbf{cover crops} & 0.364086 & 0.396418 \\
%  \textbf{water type} & 0.742097 & 0.928905 \\
%  \textbf{profitable} & 0.705882 & 0.719737 \\
%  \textbf{irrigation type} & 0.841845 & 0.847554 \\
%  \textbf{giregion} & 0.505824 & 0.568242 \\
%  \textbf{irrigation energy} & 0.746293 & 0.836405 \\
%  \textbf{data year id} & 0.422003 & 0.518059 \\ \bottomrule
%  \end{tabular}
%  \end{table}

%%%%%%%%%%%%%%%%%%%%%
% Points to address
% 
\section{Discussion}

Several physical parameters such as climate, geology and soil are predetermined by a vineyard's location; making it a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. The association between yield and region is demonstrated by its position as fourth most occurring variable within the nodes of the XGBoosted ensemble which determined region (see Figure \ref{fig:region_sankey}). The association with area and region is likely a connection to the change in land costs, with inland Australian areas (particularly of lower rainfall) being substantially cheaper to buy than coastal regions, allowing larger areas to be purchased \citep{willchancellorMeasuringAustralianBroadacre2019}.
\par
Regions with lower land costs are also warmer \citep{willchancellorMeasuringAustralianBroadacre2019}, which is known to be beneficial in hastening the ripening process of winegrapes \citep{webbObservedTrendsWinegrape2011}. Warmer regions are also associated with lower quality grapes, caused largely due to this hastened ripening \citep{botting1996canopy}. In general warmer regions have been associated with lower yields due to their generally lower rainfall, which can be mitigated through applying excess water \citep{campsGrapeHarvestYield2012}. It is likely that the combination of larger vineyards with higher water use is a determining factor in classifying regions which favour larger production of lower quality grapes; reflected through the variables' importance of water use in the XGBoost ensemble. The practice of utilising larger quantities of water for inland Australian wine crops is partly reflected in the prior use of flood style irrigation to saturate soil \citep{bgcoombeGrapeBerryDevelopment2004}. This classification can be contrasted with other warmer regions of higher rainfall that use the warmer climate to concentrate their grapes, increasing the flavour profile (and thus quality) \citep{goodwinijeriepRegulatedDeficitIrrigation1992,mgmccarthyEffectCropLoad1986}. This is possibly the connection between the presence of the Hunter Valley within the XGBoost ensemble that determined profit (see Figure \ref{fig:profit_sankey}). With this connection reflecting the restriction of possible strategies employable by winegrowers between different regions.
\par
In part some winegrowing strategies are restricted simply through access to water resources, being reflected through the region classification tree (see Figure \ref{fig:region_tree}). Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops unlike most coastal regions. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region. Where, the need to pressurise irrigation systems from river water or to generate power would require larger amounts of diesel and petrol.
\par
Operational costs showed similar importance across fuel, water and tractor use. The dominating factor of area likely played a large part in determining how costly a tractor pass would be, or in defining the ratio of water applied to the amount of vines. The node frequency was high for area but much lower in general across the other variables, which could indicate the need to be more circumstantial in determining operational costs. Although it was attempted to capture the complexity between how variables interacted when determining operational costs (see Figure \ref{fig:operating_costs_sankey}), it is likely yet more complicated still. An example of how interrelated operational costs can be, is the optimisation of tractor passes being shown to reduce energy use in vineyards, decreasing running costs, as well as reducing soil compaction \citep{capelloEffectsTractorPasses2019}. 
\par
Decisions made on the ground have far-reaching effects and are difficult to completely capture. Greater tractor use as a preventative measure for occurrences such as disease, may incur higher operational costs but could be critical in preventing long term losses. With factors such as erosion and soil health being difficult to capture but also influenced by tractor use \citep{capelloEffectsTractorPasses2019,capelloPermanentCoverSoil2020}. Although, performing well in $R^2$, the ability to predict operational costs is limited by the variables incorporated. Reductions in fuel, water and tractor use are obvious methods to reduce operational costs but not necessarily achievable decisions. Without fully capturing more granular activities such as the specifics of what fuel was used for, it is hard to determine what decisions specifically influence the operational costs.
\par
Although less important in the XGBoost ensembles for profit, the variables: cover crops, fungicide spraying and slashing are likely linked to broad environmental properties of regions (see Figure \ref{fig:region_sankey} and \ref{fig:profit_sankey}). Rainfall being related to fungal growth and disease, as well as weeds. With cover crops being an effective and sustainable method to alleviate these issues \citep{delpuechAdaptingCoverCrop2018}. It is difficult to extrapolate findings to these methods and the reason for their use due to the broad and varying definition of the regions. Utilising the Geographical Indicator regions defined by Wine Australia \citep{wineaustraliaWineAustraliaOpenData2021} is a limitation, as it is too broad to fully capture a vineyards location and its influence on more granular variables. The reasoning for using approaches such as cover crops can be widely varying. Where, a cover crop may be employed to help increase soil water retention, reduce erosion, increase biodiversity and reduce weeds \citep{capelloEffectsTractorPasses2019,capelloPermanentCoverSoil2020,delpuechAdaptingCoverCrop2018}. However, cover crops can introduce competition with grapevines and may reduce yield depending upon the plants used and the density of the cover crop \citep{goslingLongtermChangesSoil2005,monteiroInfluenceCoverCrop2007}. A more granular definition of region may help to better discern the differences in practices, and the reason for employing them. More sophisticated models, specifically those that utilise expert opinion, may also help to capture and address the decision making process. An example is the optimisation of fungicide sprays using Bayesian models that forecast disease risk \citep{luDiseaseRiskForecasting2020}.

% In particular There is the potential that the types of herbicides used also have a long term effect on crops, reducing the presence of microorganisms and soil health, making the area more prone to disease in the long run, becoming dependent on these sprays (Coll et al., 2011; Gosling and Shepherd, 2005).

% The classification tree shows a likely change in avaialble infrastructure across the years, with mroe current years being associated with pressurised water and more slashing and herbicide passes.

% The availability of solar panels for electrical irrigation and electrical irrigation in general

% Electricity is predominantly used for pumping and irrigation in vineyards \citep{longbottomRoleVineyardPractices2015}

% Fungicides are likely associated with higher preventive sprays when disease breaks out.

% Slashing passes are likely weed outbreaks or yearly cycles?

% %% Climate change

% %% Pests Insects and weeds
% %% Disease

% %% Electricity use and reasons for (connect to year)
% %% Fuel use and what it is used for

% Operational costs saw the only occurrence of renewable resources being included in the ten most important variables for its XGBoost ensemble.

% %% Address yield and how predictable it is
% %% different sales markets and performance?
% %% Reasons for profit?

% The winegrowing industry holds significant importance for Australia and its economy. There exists many challenges that the industry has to contend against, 
% with disease from sources such as Mildew and Botrytis being a considerable one (Cole, 2010; Magarey et al., 1994).

The disparity in accuracy between profit and operational costs is reflective of the complexity in trying to address challenges such as climate change, disease and changing market demands \citep{wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022}. The difference between turning a profit or loss is dependent on decisions made and chance. The difference between vineyards that make profit and those that do not could be a multitude of factors including differences in farming practices not captured within this study. Some decisions leading to latent effects such as large scale soil deposition in extreme rain events can be caused by soil compaction due to overworking a vineyard \citep{capelloPermanentCoverSoil2020}.

\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Prior studies have shown that decisions can also have long-lasting positive effects at the cost of short term negatives. In particular the use of cover crops and remedial soil techniques offer such as trade.

% with well established a cover crops requiring greater water resources to maintain but offering more protection in return (Capello et al., 2019; Delpuech and Metay, 2018; Gosling and Shepherd, 2005; Monteiro and Lopes, 2007).

% Prior studies have placed an emphasis on optimisations of fungicide sprays through the development of Bayesian models to forecast disease risk (Lu et al., 2020). This analysis investigates at the synergy between spray strategies as a proxy of fuel use to different types of water sources and sustainable strategies with an emphasis on the use of cover crops; allowing for the modelling of interactions between the use of multiple strategies. With the need to balance yield, quality, and combat adversities such as disease; the creation of tools to inform decisions and assist growers with warnings of disease risks is becoming crucial in ensuring sustainable and profitable wine production (Abbal et al., 2016).

% Soil is an important and ongoing consideration for vineyards and interacts with every other practice in various ways at different time scales. For example, cover crops have been shown to be detrimental for soil health in the short term, giving an initial reduction in soil potassium and phosphorus concentrations and no change in nitrogen levels (Gosling and Shepherd, 2005). Conversely, in longer time frames the presence of a cover crop can induce an increase in microorganisms, which can excrete phosphates and potassium, regenerating the soils chemical balance and helping to introduce further organic nitrogen (Coll et al., 2011). The studies that showed this were based in two different countries of similar climate but could have been subject to other underlying conditions not measured.

% When implementing practices such as cover crops the extent of the practice, the compounding effects and potential alternatives need to also be considered. Alternative options are always available such the use of mulch and wood chips to increase soil health and water retention in place of more involved processes such as crop rotation (Rössert et al., 2022). Crop rotation offers greater benefits than other soil management plans (Brock et al., 2011), however this is often not a viable option for many vineyards although is common practice in some places (Russo et al., 2021). The need to look at the holistic outcomes and interactions of these practices is paramount, however with the existence of many different practices, the outcomes due to interactions are not always known; one such consideration is the use of fungicide and its potential to build up copper, causing a reduction of microorganisms in the soil. Linking copper build up to any particular cause is a difficult endeavour due to the need for multiple reliable soil samples which are equally effected by the same conditions, within soil (Wightwick et al., 2010).

% Reasons for operational costs (connect to disease and pests)

% There are several environmental concerns that affect viticulture, including loss of soil quality, lack of rain, hail, disease, fire, and frost; with climate change exacerbating these issues. In 2020, 40,000 tonnes of grapes were lost across 18 different wine regions due to bush fires and smoke taint; the predicted incidence of wildfires is expected to increase (Canadell et al., 2021). In comparison to countrywide pressures such as drought, this damage made up only 3\% of the total amount of grapes for that year; although acknowledged as a considerable loss on an individual basis, it was deemed to be only a minor national concern by Wine Australia when compared to other environmental pressures such as drought (Wine Australia, 2020).

% In rainfed areas due to the lack of irrigation possibilities The result would be a shortening of the ripening period, with harvest occurring during the period with high temperatures, which could have a negative impact on wine quality (Salazar Parra et al. 2010; Duchne and Schneider 2005; Jones and Davis 2000) and yield (Mira de Ordua 2010; Iglesias et al. 2010).

% Climate change in the future might move the north and south latitude boundaries of areas suitable for good quality wines (Schultz and Jones 2010), and could even lead to improvements in fruit production and quality in some areas (Olesen and Bindi 2002). However, other areas may be negatively affected by high temperatures and water stress due to a reduction in the amount of water available.

% %% Grape quality
